A generalized definition of multidimensional item response theory parameters

### 2024-09-13 output/Main_text.Rmd
Reduces abstract to 199 words
Maximum permitted by Psychometrika is 200 words (https://www.cambridge.org/core/journals/psychometrika/information/author-instructions/preparing-your-materials)

---
title: "A generalized definition of multidimensional item response theory parameters"
output:
  officedown::rdocx_document:
    tables:
      style: APA_Like_style
    mapstyles:
      Body Text: ['First Paragraph', 'Abstract']
    base_format: bookdown::word_document2
    reference_docx: ../www/Template.docx
    number_sections: no
    keep_md:         no
    fig_width:       4
    fig_height:      4
abstract: |
  Modern measurement theory demands that
  Multidimensional Item Response Theory models accurately represent
  covariance spaces with correlated dimensions and/or non-standard variances.
  As they are applied in the non-cognitive domain as well,
  they also need to model negatively-keyed items accurately and interpretably.
  Henceforth we generalize the multidimensional discrimination
  [@reckase_discriminating_1991] and difficulty [@reckase_difficulty_1985]
  parameters to account for those two phenomena.
  We do so by applying Reckase's [-@reckase_difficulty_1985] method
  in a strictly algebraic sense to the Multidimensional 2-Parameter Logistic
  Model, represented in a latent space with an arbitrary basis, and
  then defining such basis to be a concrete geometrical representation of the
  phenomena we intend to measure. This results in three different versions of
  the multidimensional parameters: The original one, based on the item
  parameters solely, one that incorporates the covariance structure of the
  latent space, and a third one that uses the correlation structure instead.
  Importantly, we find there is a test space where
  the items should be properly represented, which must be differentiated from
  the latent space itself.
  Following @ackerman_creating_1994, we also provide a geometrical
  representation based on these parameters in the test space.
  We apply our results to examples from the literature
  to illustrate the pertinence of these generalized parameters to get an
  accurate representation of the measurement properties of the items.
  We recommend using the version that uses the latent covariance structure
  for describing the properties of the parameters,
  and the one based on the correlation structure for graphical representation.
  Finally, we discuss the implications of this generalization for
  other multidimensional IRT models
  and the parallels of our results in common factor model theory.
keywords: |
  Multidimensional IRT, 2-Parameter Logistic model,
  multidimensional item discrimination, multidimensional item difficulty,
  item vector representation, test space
bibliography: [../www/Multidimensional-parameters-MCLM.bib, ../www/packages.bib]
csl:          ../www/apa-old-doi-prefix.csl
editor_options: 
  chunk_output_type: console
---

>>>>

---
title: "A generalized definition of multidimensional item response theory parameters"
output:
  officedown::rdocx_document:
    tables:
      style: APA_Like_style
    mapstyles:
      Body Text: ['First Paragraph', 'Abstract']
    base_format: bookdown::word_document2
    reference_docx: ../www/Template.docx
    number_sections: no
    keep_md:         no
    fig_width:       4
    fig_height:      4
abstract: |
  In this paper, we generalize the multidimensional discrimination (MDISC) and
  difficulty (MID) parameters in the Multidimensional 2-Parameter Logistic model
  to account for non-identity latent covariances and negatively-keyed items.
  We apply Reckase's maximum discrimination point method to define them in an
  algebraic sense in an arbitrary basis, and then defining such basis to be a
  geometrical representation of the measured construct.
  This results in three different versions of the parameters: The original one,
  based on the item parameters solely, one that incorporates the covariance
  structure of the latent space, and one that uses the correlation structure
  instead. Importantly, we find that the items should be properly represented in
  a test space, distinct from the latent space.
  We also provide a procedure for the geometrical representation of the items in
  the test space, and apply our results to examples from the literature to get a
  more accurate representation of the measurement properties of the items.
  We recommend using the covariance structure version for describing the
  properties of the parameters, and the correlation structure version for
  graphical representation.
  Finally, we discuss the implications of this generalization for other
  multidimensional IRT models and the parallels of our results in common factor
  model theory.
keywords: |
  Multidimensional IRT, 2-Parameter Logistic model,
  multidimensional item discrimination, multidimensional item difficulty,
  item vector representation, test space
bibliography: [../www/Multidimensional-parameters-MCLM.bib, ../www/packages.bib]
csl:          ../www/apa-old-doi-prefix.csl
editor_options: 
  chunk_output_type: console
---
